\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{setspace}
\usepackage{enumitem}

\setstretch{1.5}

\title{\textbf{Rent Agreement}}
\date{}
\begin{document}

\maketitle

This Rent Agreement is made on \textbf{\today}, between:

\textbf{Landlord:} Mr./Ms. \underline{\hspace{8cm}}\\
Address: \underline{\hspace{12cm}}

\textbf{AND}

\textbf{Tenant:} Mr./Ms. \underline{\hspace{8cm}}\\
Address: \underline{\hspace{12cm}}

\section*{1. Property}
The landlord agrees to rent out the property located at:\\
\underline{\hspace{16cm}}

\section*{2. Term}
The rental term shall begin on \underline{\hspace{5cm}} and end on \underline{\hspace{5cm}}, unless terminated earlier according to this agreement.

\section*{3. Rent}
The monthly rent shall be Rs. \underline{\hspace{3cm}} payable on or before the 5\textsuperscript{th} day of each month.

\section*{4. Security Deposit}
The tenant shall pay a refundable security deposit of Rs. \underline{\hspace{3cm}} at the time of signing this agreement.

\section*{5. Maintenance and Utilities}
\begin{itemize}[noitemsep]
    \item The tenant shall keep the premises clean and in good condition.
    \item Utilities (electricity, water, etc.) shall be paid by the tenant unless otherwise agreed.
\end{itemize}

\section*{6. Termination}
Either party may terminate this agreement by giving \underline{\hspace{3cm}} days’ written notice.

\section*{7. Governing Law}
This agreement shall be governed by the laws of the State of \underline{\hspace{5cm}}.

\vspace{2cm}

\noindent
\textbf{Landlord Signature:} \underline{\hspace{7cm}} \hfill Date: \underline{\hspace{2.5cm}}\\[1cm]
\textbf{Tenant Signature:} \underline{\hspace{7cm}} \hfill Date: \underline{\hspace{2.5cm}}

\end{document} 
